Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-06 Manuscript/manuscript.tex
Improved simulation details

@@

MD simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 2018). 
The simulation parameters used in this work are summarized in Table~\ref{tbl:mdpar}. 
A comprehensive list of simulaitons used in this work is in Table~\ref{tbl:sim-list}.

@@

For deposited trajectories and parameter files see 
Refs.~\citenum{TBA}.
\todo{Joe: Upload trajectories and add references here.}

>>>>

MD simulations were performed using the GROMACS 2018 \cite{Abraham15} simulation package. 
The simulated system consisted of lipids (POPC and POPS) forming a single lipid bilayer,
an amount of water molecules comparable to the hydration levels in experiments, 
\todo{Check this claim.}
and concentrations of ions (\ce{K^+}, \ce{Na^+}, \ce{Ca^{2+}} and \ce{Cl^{-}})
in an orthorhombic simulation box with periodic boundary conditions. 
The simulation parameters used in this work are summarized in Table~\ref{tbl:mdpar}. 
A comprehensive list of simulations used in this work is in Table~\ref{tbl:sim-list}.

We used the SPC/E~\cite{Berendsen1987} water model 
and ECC-ions \cite{martinek17, kohagen16, Pluharova2014} 
for the simulations with ECC-lipids.
Force field parameters for POPC were taken from Ref.~\citenum{melcr18}. 
The ECC-POPS model as derived again from the Lipid14 force field~\cite{dickson14, lipid17-future}, as was described above.
For a direct comparison, 
we also performed simulations with the Lipid14 model~\cite{dickson14},
the TIP3P water model~\cite{jorgensen83}, 
and ion models by Dang and coworkers~\cite{smith94,chang1999,dang2006}.

For deposited trajectories and parameter files see Refs.~
\todo{Joe: Upload trajectories and add references here.}

@@

@@
